Manuscript Figures for Genome Biology

### 2018-06-04 manuscript_figures/manuscript_figures.Rmd
Fix typo in grepl commands to subset uninformative covariate sb objs

```{r Figure2}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("yeast", objects) & 
                   grepl("de5", objects) & 
                  !grepl("_uninfCov", objects)] 
de5 <- readRDS(file=resfile)
excludeSet <- c("unadjusted", "bl-df02", "bl-df04", "bl-df05")
res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.10, 0.01))

@@

# non-null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|null|polyester"), dataset) &
            !grepl("scRNAseq", casestudy) &
            !grepl("_uninfCov", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

@@

### RNA-seq
```{r}
# by dataset
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("polyester|yeast"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                excludeMethods = NULL, Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("RNA-seq")
ggsave(file.path(outdir, "FigureS4.pdf"), width=4, height=4)
```

@@

```{r}
# non-null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|polyester|null|_uninfCov"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

@@

# null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|polyester|de|_uninfCov"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

@@

```{r}
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|yeast|null|_uninfCov"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

@@

# null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|yeast|de"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

>>>>

```{r Figure2}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("yeast", objects) & 
                   grepl("de5", objects) & 
                  !grepl("-uninfCov", objects)] 
de5 <- readRDS(file=resfile)
excludeSet <- c("unadjusted", "bl-df02", "bl-df04", "bl-df05")
res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.10, 0.01))

@@

# non-null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|null|polyester"), dataset) &
            !grepl("scRNAseq", casestudy) &
            !grepl("-uninfCov", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

@@

### RNA-seq
```{r}
# by dataset
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("polyester|yeast"), objects) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                excludeMethods = NULL, Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("RNA-seq")
ggsave(file.path(outdir, "FigureS4.pdf"), width=4, height=4)
```

@@

```{r}
# non-null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|polyester|null|-uninfCov"), objects) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

@@

# null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|polyester|de|-uninfCov"), objects) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

@@

```{r}
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|yeast|null|-uninfCov"), objects) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

@@

# null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|yeast|de"), objects) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))
